%====================
% EXPERIENCE A
%====================
\sectiontitle{AI Machine Learning Data Annotator (On Call/Remote)}{September 2024 --- Present}
\subtext{Outlier \hfill Toronto, ON}
\begin{zitemize}
\item Built and optimized scalable training code, improving AI model precision by 12\% increasing efficiency.
\item Diagnosed API and input failures affecting model outputs, reducing response errors and improving reliability.
\item Enhanced contextual reasoning in ML algorithms through iterative tuning, improving response relevance.
\item Collaborated using Python to assess and correct model outputs, improving result accuracy and QA.
\item Implemented prompt engineering techniques optimizing model responses, reducing task completion time by 30\%.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\sectiontitle{Solo Software Developer}{January 2022 --- Present}
\subtext{Freelancer \hfill Toronto, ON}
\begin{zitemize}
\item Improved reservation flow and UX, showcasing booking confirmation speed improvements by \textasciitilde28\% .
\item Streamlined booking management tasks and enhanced data visibility through interactive dashboards.
\item Boosted user engagement by enabling intuitive map interaction and persistent city data saving.
\item Enhanced audio transcription efficiency for users, reducing manual work by \textasciitilde38\%.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\sectiontitle{Career Break / Pursued academic and immigration goals}{March 2020 --- November 2021}
\subtext{Accomplishments \hfill Aracaju, Brazil}
\begin{zitemize}
\item Achieved college-level English proficiency while awaiting a Canadian study permit during the COVID-19 pandemic.
\item Used visa delay period to upskill through self-study reinforcing adaptability and long-term career focus.
\item Joined virtual meetings and remote projects during travel limits, improving teamwork for global remote work.
\item Strengthened technical and soft skills, demonstrating adaptability, discipline, and commitment to long-term goals.
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\sectiontitle{Career Break / Cultural and language exchange in Canada}{January 2020}
\subtext{Accomplishments \hfill Toronto, ON}
\begin{zitemize}
\item Relocated to Canada to invest in English communication skills and adapt to a new cultural integration.
\item Completed over 300 hours of English study, participated in immersive language programs.
\item Immersed in Canadian culture and tech ecosystem by attending professional events and community meetups.
\item Engaged in interprovincial travel to experience Canada’s cultural diversity firsthand, developing cultural fluency.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
\sectiontitle{Senior Software Developer}{January 2013 --- September 2018}
\subtext{3Tecnos - Technology Generating Business \hfill Aracaju, Brazil}
\begin{zitemize}
\item Reduced invoice registration time by 10\% through C\# code optimization in ERP Supply Chain module.
\item Implemented validation routines to ensure inventory accuracy and compliance with municipal regulations.
\item Automated inventory audit processes, reducing discrepancies by 94\% and enhancing data accuracy.
\item Analyzed inventory trends to identify cost-saving opportunities, resulting in an 8\% reduction costs .
\item Optimized SQL Server stored procedures, reducing inventory report processing time by 5\% .
\end{zitemize}

%====================
% EXPERIENCE E
%====================
\sectiontitle{Technical Support Analyst}{May 2009 --- October 2012}
\subtext{Hexagon (Client: Integrated Center for Public Safety Operations) \hfill São Paulo, Brazil}
\begin{zitemize}
\item Maintained 98.9\% system uptime, ensuring uninterrupted support for emergency responders.
\item Enabled 25\% faster reporting, improving coordination and decision-making during emergencies .
\item Boosted system usability and efficiency, supporting over 100 users across departments.
\item Reduced query time achieving 30\% faster data processing enhancing situational awareness for dispatchers.
\item Diagnosed hardware, software, and network issues and installed/configured CAD systems.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
\sectiontitle{Senior Systems Analyst}{January 2008 --- April 2009}
\subtext{Indra Brazil Solutions \& Tech Services LTDA \hfill Aracaju, Brazil}
\begin{zitemize}
\item Delivered 5+ fully functional tools, streamlining workflows for internal departments and reducing manual effort.
\item Increased task efficiency by 25\%, freeing up officers’ time for high-priority responsibilities .
\item Expanded accessibility and reduced citizen wait times by 40\% across the region.
\item Improved app performance and stability, reducing load times by 50\% and increasing user satisfaction.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
\sectiontitle{Senior Systems Analyst}{January 2003 --- January 2008}
\subtext{Impact Labor (Client: Brazilian Federal Police Department) \hfill Aracaju, Brazil}
\begin{zitemize}
\item Ensured high system availability and reliability, supporting daily operations for over 100 employees.
\item Achieved a 100\% successful migration with zero downtime, lowering database licensing expenses.
\item Built a PHP-based ERP system that automated daily operations, cutting manual workload by 40\%.
\item Improved internal workflows and communication, reducing task redundancy and manual data entry
\end{zitemize}